---
title: "My Everesting Journey"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

<style type="text/css">     
.navbar {
  background-color:#2a2a2b;
  border-color:#2a2a2b;
}
</style>   

```{r setup, include=FALSE}
library(flexdashboard)
source('everesting.R') 
```
  
> <font size = "3px">
The concept of [Everesting](https://www.everesting.cc/) is to pick any hill, anywhere in the world and complete repeats of it in a single activity until you climb 8,848m – the equivalent height of Mt Everest.⛰️</font>    
> <font size = "3px">
On 03.06.2023 I finished [my first everesting](https://www.strava.com/activities/9198965017/overview) by riding
my MTB up and down 42 times to the iconic János-hill of Budapest. It took me 27 hrs (non-stop) to finish. I am the first rider from Hungary to accomplish this feat on an off-road track earning the first [Soil Badge](https://hof.everesting.com/hall-of-fame/hall-of-fame-details?uuid=a226dd85-6880-4e18-b762-1ae4717c836a&mt=0) for my country.💣💥</font>    
> <font size = "3px">
After each turn I note down how I feel on a scale of 0-9 so to craft the following story-telling visualization afterwards:</font>  
    
row {data-height=400}
-----------------------------------------------------------------------

### All {.no-padding .no-title}

```{r}
strmgrph
```


row {data-height=50, .no-padding}
-----------------------------------------------------------------------

> <font size = "2px"> Created by: [Komjáti Bálint](https://www.balint-komjati.hu/) </font>
